Proportional Occupancy

### 2021-06-30 R/PropOcDataThor.Rmd
fixed propOc function to map and take tiffs

```{r functions to get data}
#using the new 3D script with capped spheres.
source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
GetPropOcData<-function(sample, timepoints, positions){
  #folder<- paste0('/media/jbarraza6/Seagate Backup Plus Drive/Good images/',sample,'/images1')
  folder<- paste0('~/Desktop/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed1')
  growthDf<-data.frame()#data frame to add all timepoints and positions
  fileList<-list.files(path = folder, full.names = TRUE)
  print(folder)
  for (position in 2:positions){
    currentPosition<-fileList[grep(paste0("p",position,"_"),fileList)]
    print(paste0('analyzing position ', position))
    for (timepoint in 0:timepoints){
      currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
      dataTimePoint<-AllDataPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
                                     xydimSearch=114,zdimSearch = 70, sampleSize=1000,xyRealDim=0.264,
                                     zRealDim = 0.44, pipeBinSize = 1)
      dataTimePoint$TimePoint <- timepoint
      dataTimePoint$Position <- position
      growthDf<-rbind(growthDf,dataTimePoint)
      }
    }
  return(growthDf)
  }
GetSlice<-function(idx){
  if (idx<10){num = paste0(0,idx)}
  else
  {num = idx}
  return(num)}
```

>>>>

```{r functions to get data}
#using the new 3D script with capped spheres.
source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') 
GetPropOcData<-function(sample, timepoints, positions){
  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
  growthDf<-data.frame()#data frame to add all timepoints and positions
  fileList<-list.files(path = folder, full.names = TRUE)
  print(folder)
  for (position in 2:positions){
    currentPosition<-fileList[grep(paste0("p",position,"_"),fileList)]
    print(paste0('analyzing position ', position))
    for (timepoint in 0:timepoints){
      currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
      dataTimePoint<-AllDataPipeline(SlicesTo3D(redVolume),SlicesTo3D(greenVolume), 
                                     xydimSearch=114,zdimSearch = 70,
                                     sampleSize=1000,xyRealDim=0.264,
                                     zRealDim = 0.44, pipeBinSize = 1)
      dataTimePoint$Condition <- 
      dataTimePoint$TimePoint <- 
      growthDf<-rbind(growthDf,dataTimePoint)
      }
    }
  return(growthDf)
}

GetPropOcData<-function(sampleName, xyDim,zDim){
  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  sampleFolder<-paste0(parentFolder, sampleName)
  attrList<-str_split(sampleName,"_")[[1]]
  fileList<-list.files(path = sampleFolder, full.names = TRUE)
  greenImg<-fileList[grep("G_",fileList)]
  redImg<-fileList[grep("R_",fileList)]
  propOcData<-AllDataPipeline(SlicesTo3D(redImg),SlicesTo3D(greenImg), 
                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
                                     sampleSize=10,xyRealDim=xyDim,
                                     zRealDim = zDim, pipeBinSize = 1)
  propOcData$Condition <- attrList[1]
  propOcData$TimePoint <- attrList[2]
  propOcData$Replicate <- attrList[3]
  write.csv(propOcData, paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
}

testGetPropOcData<-GetPropOcData("mono_d1_01", .415,.52)
testPmap<-pmap(list(metaData.df$SampleCode, metaData.df$xyDim, metaData.df$Zdim),GetPropOcData)
boundPmapTest<-bind_rows(testPmap)

testGrep<-list.files(path = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
testGrepG<-testGrep[grep("G_",testGrep)]

GetSlice<-function(idx){
  if (idx<10){num = paste0(0,idx)}
  else
  {num = idx}
  return(num)}

Slices2threeD<-function(fileList){
  image1<-as.array(readImage(fileList[1], convert = TRUE))#read first image to get its dimensions
  image3D <- array(0, c(dim(image1)[1], dim(image1)[2], length(fileList)))#preallocate array for image given using image dimensions
  for(i in 1:length(fileList)){#keep in mind that it is not zero-index
    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
    image3D[,,i]<-as.array(readImage(fileList[i], convert = TRUE))
  }
  return(image3D)
}
testSlices2threeD<-Slices2threeD(testGrepG)
testGrepG[1]
testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
